---
title: "Bechdel Test data (Tidy Tuesday - March 9, 2021)"
author: "Ryan Woodbury"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(tidytuesdayR)
```

```{r data}
#tuesdata <- tidytuesdayR::tt_load(2021, week= 11)

raw_bechdel <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/raw_bechdel.csv')
movies <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-09/movies.csv')
```

```{r, glimpse, eval = F}
glimpse(raw_bechdel)
glimpse(movies)
```

Make left join to prioritize the Bechdel data.

```{r join}
bechdel_movies <- raw_bechdel %>% 
  full_join(movies, by = c("imdb_id" = "imdb_id", "year" = "year", "title" = "title"))
```


```{r, eval = F}
glimpse(bechdel_movies)
```

```{r check, eval = F}
## prioritize the bechdel data

raw_bechdel %>% 
  filter(year == 2000) %>% 
  count() # 152

movies %>% 
  filter(year == 2000) %>% 
  count() # 63

bechdel_movies %>% 
  filter(year == 2000) %>% 
  count() # 152
```

Who are the directors with the highest proportion of movies that pass the Bechdel test?

I might have to filter out those with only one movie, but we can see how many have only 1 movie directed that passes the Bechdel test.

```{r}
director_bechdel <- bechdel_movies %>% 
  filter(!is.na(director)) %>% 
  group_by(director) %>% 
  summarize(num_movies = n(),
    num_bechdel = sum(ifelse(binary == "PASS", 1, 0), na.rm = T), .groups = "keep") %>% 
  mutate(bechdel_prop = round((num_bechdel/num_movies) * 100, 2)) %>% 
  arrange(desc(bechdel_prop)) %>% 
  filter(num_movies > 1) %>% 
  select(director, bechdel_prop, num_movies)
```

```{r}
ggplot(director_bechdel, aes(bechdel_prop)) +
  geom_histogram(bins = 20)
```

There are over 50 directors that have directed more than one film that have a 100% pass-rate on the Bechdel Test. This is a simple graph, but due to the fact that most directors are excluded, we can explore another set of variables that might provide some more predictive power.