---
title: "Deforestation (Tidy Tuesday - April 6, 2021)"
author: "Ryan Woodbury"
date: "4/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading libraries

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse) # data manipulation
library(tidytuesdayR) # Tidy Tuesday data
library(tidymodels) # Modeling!
library(stacks) # Ensemble methods
library(gt) # html tables
library(DataExplorer)
library(SmartEDA)
theme_set(theme_classic())
```

Getting the data

```{r message=FALSE, warning=FALSE}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

# tuesdata <- tidytuesdayR::tt_load('2021-04-06')
# tuesdata <- tidytuesdayR::tt_load(2021, week = 15)

#forest_change <- tuesdata$forest_change

# Or read in the data manually

forest <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-06/forest.csv')
forest_area <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-06/forest_area.csv')
brazil_loss <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-06/brazil_loss.csv')
soybean_use <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-06/soybean_use.csv')
vegetable_oil <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-04-06/vegetable_oil.csv')
```

Quick exploration of data

Comparing DataExplorer, SmartEDA, and skimr

The default report creator functions from `DataExplorer::` (`create_report()`) and `SmartEDA::` (`ExpReport()`) don't work on these smaller data sets, but `skimr` works fine. The `psych::` package also has a data explorer/summarizer as well.

I can select what I want built from `DataExplorer` or `SmartEDA`, but I cannot render a full html report.

```{r}
summary(forest)
glimpse(forest)
#DataExplorer::create_report(forest)
introduce(forest)
plot_intro(forest)
plot_missing(forest)
#plot_bar(forest)


skimr::skim(forest)
```

```{r}
summary(forest_area)
glimpse(forest_area)
SmartEDA::ExpData(forest_area, type = 1)
SmartEDA::ExpData(forest_area, type = 2)
#SmartEDA::ExpReport(forest_area, op_file = "forest_area_report.html", sc = 2, sn = 2)

ExpNumStat(forest_area)
```

