---
title: "Mario Kart (Tidy Tuesday)"
author: "Ryan Woodbury"
date: "5/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I would love to build a visualization that shows the different tracks based on their average speed of professional racers in 3-lap races.

### Load the libraries
```{r}
library(tidyverse)
library(lubridate)
library(ggiraph)

theme_set(theme_classic())
```


### Get the data

```{r}
records <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-25/records.csv')
drivers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-25/drivers.csv')
```

Records data

```{r}
glimpse(records)
summary(records)
```

```{r}
glimpse(drivers)
summary(drivers)
```



I want to know which track has the fastest three-lap record and fastest one-lap record, non-shortcut, NTSC time. Maybe add a tooltip that includes how long it took break the record, and who holds the current record.


```{r}
records_clean <- records %>% 
  filter(type == "Three Lap",
         shortcut == "No",
         #system_played == "NTSC"
         )
summary(records_clean)
```

```{r}
fastest_records <- records_clean %>% 
  group_by(track) %>% 
  summarise(fastest_time = min(time)) %>%
  ungroup() %>% 
  left_join(records_clean, by = c("track" = "track", "fastest_time" = "time")) %>% 
  #mutate(fastest_time = fastest_time/60) %>% 
  ggplot() +
  geom_point_interactive(aes(fastest_time, fct_reorder(track, fastest_time), color = track, tooltip = paste0("Track name: ", track,
                                                                                                             "<br>Record Holder: ", player,
                                                                                                             "<br>Time: ", time_period,
                                                                                                             "<br>Duration of Record: ", record_duration,
                                                                                                             "<br>Record made: ", date)), show.legend = F, size = 2) +
  scale_y_reordered() +
  scale_x_time() + 
  #scale_color_brewer(palette = "Spectral") +
  labs(x = "Time",
      y = "Track Name",
      title = "Is Rainbow Road Really That Difficult?",
      subtitle = "Fastest Record Times for Each Track")

girafe(ggobj = fastest_records)
```

