---
title: "Tidy Tuesday Week 5-Plastic Pollution"
author: "Ryan Woodbury"
date: "1/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
theme_set(theme_classic())
```


# Get the Data

## Read in with tidytuesdayR package 
## Install from CRAN via: install.packages("tidytuesdayR")
## This loads the readme and all the datasets for the week of interest

## Either ISO-8601 date or year/week works!


```{r}
#tuesdata <- tidytuesdayR::tt_load('2021-01-26')
tuesdata <- tidytuesdayR::tt_load(2021, week = 5)

plastics <- tuesdata$plastics

# plastics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-26/plastics.csv')

head(plastics)
```
# quick summary of data

```{r}
summary(plastics)
```


```{r}
glimpse(plastics)
```


```{r}
plastics_long <- plastics %>%
  pivot_longer(c(empty:pvc, grand_total), names_to = "type")
```

Need to do some filtering to remove unknown parent companies.

```{r}
'%notin%' <- Negate(`%in%`)

plastics_long_filter <- plastics_long %>% 
  filter(parent_company %notin% c("Unbranded", "null", "empty", "NULL", "Grand Total")) %>% 
  filter(type != "grand_total")
```

## The name conventions of the companies are free-response and have a lot inconsistencies. For example, "Johnson & Johnson" and "Johnson and Johnson". Or "The McDonald's Coporation" and "McD" and "McDonald's" I'm sure there are many others.

```{r}
# Base R string distance
# The distance is a generalized Levenshtein (edit) distance.
# Basically, the minimal number of insertions, deletions and substitutions needed to transform one string into another.
# In the example below, 3 edits are needed (1 replacement, 2 deletions)
utils::adist("Johnson and Johnson", "Johnson & Johnson")
```

```{r}
# Base R fuzzy match
# Two Johnson and Johnson and SC Johnson are different companies
# Return the indexs for any fuzzy matches
base::agrep("Johnson and Johnson", c("Johnson & Johnson", "SC Johnson"), max=3, ignore.case = TRUE)
```

